---
title: "CSE 101 R Notebook"
output: html_notebook
---

==============================================================================================================

**Task 1:**

Take 3 inputs from the user: x, y, z. Write a program in R that prints the numbers that are multiples of both x and y  from 1 to z using loops.(while or for loop)

==============================================================================================================

```{r}

#Solution to Task 1

num_x = as.integer(readline(prompt = "Sir, please enter your first number: "))
num_y = as.integer(readline(prompt = "Sir, please enter your second number: "))
num_z = as.integer(readline(prompt = "Sir, please enter your second number: "))

for (i in 1:num_z) {if (i %% num_x == 0 & i %% num_y == 0) {cat(paste(i,""))}}

```

==============================================================================================================

**Task 2:**

Write a program in R that takes a number, n and prints a triangle with n steps like the following:

Hint: Use cat function instead of print() without a new line.

**Sample Input:**

6

**Sample Output:**

**\***

**\*\***

**\*\*\***

**\*\*\*\***

**\*\*\*\*\***

**\*\*\*\*\*\***

==============================================================================================================

```{r}

#Solution to Task 2

num_x = as.integer(readline(prompt = "Sir, please enter your first number: "))

for (i in 1:num_x) {cat(paste(replicate(i,"*")), "\n")}

```

==============================================================================================================

**Task 3:**

Write a program in R that takes a string input from the user and prints the characters of odd numbered indices using a loop.

**Sample Input:**

Programming

**Sample Output:**

P

o

r

m

i

g

**Sample Input:**

Computer

**Sample Output:**

C

m

u

e

==============================================================================================================

```{r}

#Solution to Task 3

user_input = readline(prompt = "Sir, please enter your desired text: ")

for (i in 1:nchar(user_input)) {if (i %% 2 == 0) {cat(substr(user_input, i, i),"\n")}}

```

==============================================================================================================

**Task 4:**

Write a program in R that would take an integer input from the user and display if that particular number is a prime number or not.

A number is a prime number if it is divisible only by itself and 1 (example: 2, 3, 5, 7, 11).

==============================================================================================================\

```{r}

# Solution to Task 4

user_input = as.integer(readline(prompt = "Sir, please enter your desired number: "))
flag = TRUE

for (i in 2:(user_input-1)) {if (user_input %% i == 0) {flag = FALSE}}

if (flag | user_input == 2 | user_input == 3) {cat(user_input,"is a prime number")
} else {cat(user_input,"is not a prime number")}

```

==============================================================================================================

**Task 5:**

Write a R program to update the last element with "R programming"  of the following list and prints the new list:

mylist= list("John","Denver","Max",1,2,4,8,9,11,list("Java"))

==============================================================================================================

```{r}

# Solution to Task 5

mylist= list("John","Denver","Max",1,2,4,8,9,11,list("Java"))
mylist[length(mylist)]= "R programming"
print(mylist)

```

==============================================================================================================

**Task 6:**

Write a R program to add a new item "Ford" after the third element of the given list and prints the new list of cars: 

super_cars = list("Ferrari","Audi","Porsche","Lamborghini","Nissan")

==============================================================================================================

```{r}

# Solution to Task 6

super_cars = list("Ferrari","Audi","Porsche","Lamborghini","Nissan")

super_cars = append(super_cars, "Ford", after = 3)

print(super_cars)

```

\
==============================================================================================================

**Task 7:**

Write a R program to create an array of two 3x3 matrices each with 3 rows and 3 columns from a given vector and print the second row of the first matrix of the array.

Given vector: vc1 =  c(10,11,12,13,14,15)

==============================================================================================================

```{r}

# Solution to Task 7

vc1 = c(10,11,12,13,14,15)

result_array = array(c(vc1,vc1), dim = c(3,3,2))

print(result_array[2, ,1])

```

======================================================**END**=====================================================\



\
